The Practical Application of MST

### 2021-02-17 article.Rmd
Use standardised Cronbach's alpha

The `ltm` library can be used to fit a number of dichotomous and polytomous IRT models. Its the fastest library that I've found for fitting a Rasch model. First we get some summary statistics from the data, including

@@

# return descriptive stats such as Cronbach's alpha
descript <- ltm::descript(dfTrial, chi.squared = FALSE)

# graph the frequencies of the total scores
dfFreqs <- enframe(descript$items[1:length(descript$items)],
                   name = "testscore", value = "frequency")

ggplot(data = dfFreqs) +
  geom_bar(mapping = aes(x = testscore, y = frequency), stat = "identity") +
  xlim(0, 40)
```

>>>>

The `ltm` library can be used to fit a number of dichotomous and polytomous IRT models. Its the fastest library that I've found for fitting a Rasch model. Before doing that we get some summary statistics from the data, including the Cronbach's alpha measure of covariance. Cronbach's alpha is a function of the number of items in a test, the average covariance between pairs of items, and the variance of the total score. It is defined as:

$$
\alpha = \frac{p \times \bar{r}}{1 + (p – 1)\bar{r}}
$$
Where $p$ is the number if items, $\bar{v}$ is the mean variance of each item, and $\bar{r}$ is the average of all covariances between items.

In our test we've split our items into different modules according to the skill that is being measured, so it makes sense to calculate alphas for each module, although we could also do so by stage if we wanted. We need to make sure that we remove any rows containing NA values before calculating Cronbach's alpha.

@@

# now create per-module item response data frames, remembering to remove 
# any candidates who did not take the module
dfModuleAItems <- dfTrial %>% dplyr::select(1:12) %>% na.omit()
dfModuleBItems <- dfTrial %>% dplyr::select(13:20) %>% na.omit()
dfModuleCItems <- dfTrial %>% dplyr::select(21:28) %>% na.omit()
dfModuleDItems <- dfTrial %>% dplyr::select(29:38) %>% na.omit()
dfModuleEItems <- dfTrial %>% dplyr::select(39:48) %>% na.omit()
dfModuleFItems <- dfTrial %>% dplyr::select(49:58) %>% na.omit()
dfModuleGItems <- dfTrial %>% dplyr::select(59:68) %>% na.omit()

# calculate Cronbach's alpha for each module
alphasModuleA <- ltm::cronbach.alpha(dfModuleAItems, standardized = TRUE, na.rm = TRUE)
alphasModuleB <- ltm::cronbach.alpha(dfModuleBItems, standardized = TRUE, na.rm = TRUE)
alphasModuleC <- ltm::cronbach.alpha(dfModuleCItems, standardized = TRUE, na.rm = TRUE)
alphasModuleD <- ltm::cronbach.alpha(dfModuleDItems, standardized = TRUE, na.rm = TRUE)
alphasModuleE <- ltm::cronbach.alpha(dfModuleEItems, standardized = TRUE, na.rm = TRUE)
alphasModuleF <- ltm::cronbach.alpha(dfModuleFItems, standardized = TRUE, na.rm = TRUE)
alphasModuleG <- ltm::cronbach.alpha(dfModuleGItems, standardized = TRUE, na.rm = TRUE)

# create a composite data frame and plot the alphas and the number of samples
# we'll want to focus on modules that show a low alpha and a small number of samples
# as we may want to get more trial data for these, or look at the items to make
# sure they are testing the right skill (or both)
module <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
alpha <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)

dfCronbachsAlpha <- data.frame(module, num_items, num_responses, alpha)

(dfCronbachsAlpha)
```
Ideally we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same ability.
